---
title: "response_processing"
author: "jjm-w"
date: "16/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(plotly) # to make interactive plots
```

```{r}
data <- read_csv("../data/knowledge_data.csv") # qualtrics data
actual_values <- read_csv("../data/actual_values.csv") # correct values
actual_values <- pivot_longer(actual_values, everything(), values_to = "actual_value")

# *** actual values ***
# reorder levels
actual_values$name <- factor(actual_values$name, levels = c('butter_1',
'milk_1',
'yoghurt_1',
'cheese_1',
'beef_1',
'eggs_1',
'chicken_1',
'cod_1',
'ham_1',
'tuna_1',
'pasta_1',
'apple_1',
'soy_milk_1',
'margarine_1',
'soy_yoghurt_1',
'tofu_1',
'lentils_1',
'rice_1',
'aubergine_1',
'sunflower_oil_1'))

# rename levels
levels(actual_values$name) <- c('Butter',
'Milk',
'Yoghurt',
'Cheese',
'Beef',
'Eggs',
'Chicken',
'Cod',
'Ham',
'Tuna',
'Pasta',
'Apple',
'Soy milk',
'Margarine',
'Soy yoghurt',
'Tofu',
'Lentils',
'Rice',
'Aubergine',
'Sunflower oil')

# *** df ***
# get rid of first two rows and select variable columns
df <- data.frame(data[-c(1:2),c(which(colnames(data) == "butter_1"):which(colnames(data) == "sunflower_oil_1"))])

# make variables numeric
for(i in 1:ncol(df)){
  df[,i] <- as.numeric(df[,i])
}

# make long
df_long <- pivot_longer(df, everything(), 
                        values_to = "value")

df_long$name <- as.factor(df_long$name) 

# reorder levels
df_long$name <- factor(df_long$name, levels = c('butter_1',
'milk_1',
'yoghurt_1',
'cheese_1',
'beef_1',
'eggs_1',
'chicken_1',
'cod_1',
'ham_1',
'tuna_1',
'pasta_1',
'apple_1',
'soy_milk_1',
'margarine_1',
'soy_yoghurt_1',
'tofu_1',
'lentils_1',
'rice_1',
'aubergine_1',
'sunflower_oil_1'))

# rename levels
levels(df_long$name) <- c('Butter',
'Milk',
'Yoghurt',
'Cheese',
'Beef',
'Eggs',
'Chicken',
'Cod',
'Ham',
'Tuna',
'Pasta',
'Apple',
'Soy milk',
'Margarine',
'Soy yoghurt',
'Tofu',
'Lentils',
'Rice',
'Aubergine',
'Sunflower oil')

# *** descriptives ***
# calculate mean and sd
mean <- c()
sd <- c()
for(i in 1:ncol(df)){
  mean[i] <- mean(df[,i])
  sd[i] <- sd(df[,i])
}

# make descriptives df
descriptives <- data.frame(rbind(mean,sd))
colnames(descriptives) <- colnames(df)

# make long
desc_long <- pivot_longer(descriptives, everything(), 
                          values_to = "value")
desc_final <- cbind(desc_long[1:(nrow(desc_long)/2),], desc_long[(nrow(desc_long)/2 + 1):nrow(desc_long),2])
colnames(desc_final) <- c("name","mean","sd")

# reorder levels
desc_final$name <- factor(desc_final$name, levels = c('butter_1',
'milk_1',
'yoghurt_1',
'cheese_1',
'beef_1',
'eggs_1',
'chicken_1',
'cod_1',
'ham_1',
'tuna_1',
'pasta_1',
'apple_1',
'soy_milk_1',
'margarine_1',
'soy_yoghurt_1',
'tofu_1',
'lentils_1',
'rice_1',
'aubergine_1',
'sunflower_oil_1'))

# rename levels
levels(desc_final$name) <- c('Butter',
'Milk',
'Yoghurt',
'Cheese',
'Beef',
'Eggs',
'Chicken',
'Cod',
'Ham',
'Tuna',
'Pasta',
'Apple',
'Soy milk',
'Margarine',
'Soy yoghurt',
'Tofu',
'Lentils',
'Rice',
'Aubergine',
'Sunflower oil')
```

```{r}
plot_data <- merge(desc_final, actual_values, by = "name")

# mean and sd plot
ggplot(plot_data, aes(name, mean)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd)) +
  coord_flip() +
  geom_point(data = plot_data, aes(name, actual_value), colour = "red") +
  theme_bw() +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 200)) +
  ggtitle("Plot showing your estimates compared with actual emissions") +
  labs(caption = "Black dots are your mean estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic"))

# boxplot
ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = "red", size = 2) +
  theme_bw() +
  xlab("Food item") + ylab("g CO2 equivalents") +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 200)) +
  ggtitle("Plot showing your estimates compared with actual emissions") +
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic"))

# boxplot with line separating animal and plant-based
ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = "red", size = 2) +
  theme_bw() +
  geom_vline(xintercept = 10.5, linetype = "dotted") +
  xlab("Food item") + ylab("g CO2 equivalents") +
  ggtitle("Plot showing your estimates compared with actual emissions") +
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic")) +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 200))
```
```{r more_viz}

Jo_plot_formatted<-ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = "red", size = 2) +
  theme_bw() +
  geom_vline(xintercept = 10.5, linetype = "dotted") +
  xlab("") + 
  ylab(bquote(~CO[2]~ equivalent (g))) +
  ggtitle("Your estimates vs. actual emissions") +
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic")) +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))

Jo_plot<-ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = "red", size = 2) +
  theme_bw() +
  geom_vline(xintercept = 10.5, linetype = "dotted") +
  xlab("") + 
  ylab("CO2 equivalent (g)") +
  ggtitle("Your estimates vs. actual emissions") +
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic")) +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))

Jo_plot_formatted



ggplotly(Jo_plot)






```

# change boxplot??
# add plant & animal based var -> different colour
# 5. change alpha
# 6. change how many decimals are displayed (trace?)
```{r more plotting}
# add variable source: animal, plant

vegan <- c("Pasta","Apple","Soy milk", "Margarine", "Soy yoghurt", "Tofu", "Lentils", "Rice", "Aubergine", "Sunflower oil")

df_long<-df_long %>% 
  mutate(source=name)

for (i in df_long$source)     # this doesn't work
  {
  if(df_long$source[i] %in% vegan) {
    df_long$source[i]="plant"
  } else {
     df_long$source[i]="animal"
  }
}



```

```{r order by actual impact}
actual_values<- actual_values %>% 
  arrange(desc(actual_value))

```
```{r order df_long}
#order df_long to match order of actual values
reordered_idx<-match(actual_values$name, df_long$name) # extracting indexes

df_long<-df_long[reordered_idx,] # reordering df_long to match actual-values(now ordered)

```

<<<<<<< HEAD
foss_theme<- function () { 
    theme_classic(base_size=12, base_family="Avenir") %+replace% 
        theme(
           text=element_text(family="Tahoma", size=16),
           panel.grid.major.y = element_line(colour = "grey88", size=0.1),
           panel.grid.major.x = element_line(colour = "grey80", size = 0.1),
           plot.title = element_text(hjust = 0.5),
           legend.position="none",
           plot.caption = element_text(face = "italic")
        )
=======
```{r}
actual_values<-actual_values %>% 
  mutate(source=name)

for (i in actual_values$source)     # this doesn't work
  {
  if(actual_values$source[i] %in% vegan) {
    actual_values$source[i]="plant"
  } else {
    actual_values$source[i]="animal"
  }
>>>>>>> parent of 10af3f3 (better plots)
}

```


```{r}
<<<<<<< HEAD
#plot with nicely formatted title
# 
# Jo_plot_formatted<-ggplot(df_long, aes(name, value, fill =source)) + 
#   geom_jitter( aes(fill=source, color = source), size=0.4, width = 0.1, alpha=0.5) +
#   coord_flip() +
#   geom_point(data = actual_values, aes(name, actual_value, color = source),  size = 2) +
#   scale_colour_manual(values = c("red3", "green4"))+
#   scale_fill_manual(values = c("red3", "green4"))+
#   xlab("") + 
#   ylab(bquote(~CO[2]~ equivalent (g))) +
#   ggtitle("Your estimates vs. actual emissions") +
#   labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
#   scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))+
#   foss_theme()


=======
Jo_plot_formatted<-ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = "red", size = 2) +
  theme_bw() +
  xlab("") + 
  ylab(bquote(~CO[2]~ equivalent (g))) +
  ggtitle("Your estimates vs. actual emissions") +
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  theme(plot.caption = element_text(face = "italic")) +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))
>>>>>>> parent of 10af3f3 (better plots)

Jo_plot<-ggplot(df_long, aes(name, value)) + 
  geom_boxplot() +
  coord_flip() +
  geom_point(data = actual_values, aes(name, actual_value), colour = source, size = 2) +
  theme_classic()+
  geom_vline(xintercept = 10.5, linetype = "dotted") +
  xlab("") + 
  ylab("CO2 equivalent (g)") +
  ggtitle("Your estimates vs. actual emissions") +
<<<<<<< HEAD
  labs(caption = "small dots are individual estimates, large dots are actual emissions") +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))+
  foss_theme()


```


```{r plotly_finish}

#Jo_plot_formatted

fig<-ggplotly(Jo_plot)

fig <- style(fig, hoverinfo = c("y"))
fig

htmlwidgets::saveWidget(as_widget(fig), "../images/CF_quiz.html")
htmlwidgets::saveWidget(as_widget(fig), "C:/Users/Helena/R_projects/helena_website/docs/CF_estimates.html")
=======
  labs(caption = "Boxplots are your estimates, red dots are actual emissions") +
  scale_y_continuous(limits = c(0,3000), breaks = seq(0,3000, 500))

Jo_plot_formatted


>>>>>>> parent of 10af3f3 (better plots)



```



